### 2019-03-17 papers/journal/encoding.tex
update in BMC section> 01

The molecule set is divided into Q and R-SNAREs. 
%
For clarity, we consider the first part of the bit vector as Q-SNAREs and rest as R-SNAREs.
%
An edge in the system with $M$ = 4 molecules is interpreted as a label [$M_{1}, M_{2}, M_{3}, M_{4}$]. 
%
Where $M_{1}, M_{2}, M_{3}$ are Q-SNAREs while $M_{4}$ is a R-SNARE.
%
Also, each $M_i$ can be either 0 or 1, representing the presence or absence of the $i^{th}$ molecule.
%
For example, the variable \texttt{bvEdge}[1][2][1] = 1001 represent first edge between node 1 and node 2 with molecule $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) present. 
%
Similarly, a node in the graph is also labelled as a bit vector of length $M$.   
%
We leave the graph completely arbitrary and add the constraint to enforce that the graph is k-connected. 
%

>>>>

The molecule set is divided into Q and R-SNAREs. 
%
For clarity, we consider the first part of the bit vector as Q-SNAREs and rest as R-SNAREs.
%
An edge in the system with $M$ = 4 molecules is interpreted as a label [$M_{1}, M_{2}, M_{3}, M_{4}$]. 
%
Where $M_{1}, M_{2}, M_{3}$ are Q-SNAREs while $M_{4}$ is a R-SNARE.
%
Also, each $M_i$ can be either 0 or 1, representing the presence or absence of the $i^{th}$ molecule.
%
For example, the variable \texttt{bvEdge}[1][2][1] = 1001, represents the first edge between node 1 and node 2 with molecule $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) present. 
%
Similarly, a node in the graph is also labelled as a bit vector of length $M$.   
%
We leave the graph completely arbitrary and add the constraint to enforce that the graph is k-connected. 
%
